Executive Constraints and Civil Conflict Onset

### 2020-04-29 paper.Rmd
Add section interpreting random intercepts

>>>>

TODO: grab this programmatically

#### Random Effects

There are three sets of random effects included in the regression
model. The first to be presented in figure \ref{fig:year} is the year
intercepts with 80 percent posterior credible intervals. There is no
discernible time trend in the year specific variability. The estimates
are strongly pulled towards zero as a result of the partial pooling
with upticks, such as the in the initial years of the 1990s during the
dissolution of the Soviet Union and Yugoslavia, roughly mirroring the
global incidence rate of onsets.

```{r fig.cap = "\\label{fig:year} Log-odds year intercepts - $80\\%$ CIs"}
Z_year <- extract(reg, "Z_year")
colnames(Z_year) <- { unique(final.df$year) + 1 } %>% sort

breaks <- seq(min(final.df$year), max(final.df$year), by = 4)
plot_pars(Z_year, hline = T) +
    scale_x_discrete(breaks = breaks)

```{r results = "hide"}
alpha <- extract(reg, "alpha")

alpha_s <- quantile(alpha, probs = c(0.1, 0.9)) %>% signif(3)
alpha_interval <- sprintf("[%g,%g]", alpha_s[1], alpha_s[2])
```

Figure \ref{fig:country} presents the country intercepts. Since all of
the countries cannot be easily visualized at once only the top ten and
bottom ten depicted. From the results it is clear that there is
considerably less uncertainty in the estimates for the top
countries. The intercepts for these countries are consistently above
zero meaning that the risk of civil conflict onset is higher than that
predicted solely by the other predictors. Unsurprisingly, these
countries tend to experience the highest number of civil conflict
onsets in the dataset which, conditional on the data, accounts for the
higher baseline risk. The countries at the bottom have experienced
relatively few, if any, conflict onsets relative to their values for
the other predictors. The majority of intercepts for these countries
overlap zero possibly because the global intercept is already fairly
low, `r alpha_interval` (80 percent log-odds CI).

```{r, fig.cap = "\\label{fig:country} Log-odds country intercepts - $80\\%$ CIs"}

Z_country <- extract(reg, "Z_country")
colnames(Z_country) <- unique(final.df$country_name) %>% sort

x <- apply(Z_country, 2, median) %>% order(decreasing = F)
top <- head(x, 10)
bottom <- tail(x, 10)

fn <- function(x, title) {
    plot_pars(x, hline = T) +
        coord_flip() +
        theme(axis.title.y = element_blank()) +
        ggtitle(title)
}

p1 <- fn(Z_country[, top], "Bottom 10")
p2 <- fn(Z_country[, bottom], "Top 10")

```{r results = "hide"}
gp <- extract(reg, c("rho", "eta")) %>% post_summarise(probs = c(0.1, 0.9)) %>%
    mutate(interval = sprintf("[%.3f, %.3f]", signif(`10%`, 3), signif(`90%`, 3)))
```

Finally, figure \ref{fig:peace} plots the peace year intercepts.[^gp]
The strongest effect is found in the years immediately following an
occurrence of intrastate political violence resulting in an increased
risk for an additional onset.  Approximately a decade after the last
incidence of violence, the effect is drawn towards zero. The
additional spike around approximately 30 years follows an uptick in
conflict onsets in the dataset mostly among authoritarian regimes such
as, for example, the 1989 coup d'etat overthrowing the Stroessner
regime in Paraguay, the Saur Revolution in 1978 in Afghanistan, and
the start of the Nepalese Civil War in 1996. After 30 years, the
effect of each additional year of peace tends to be negative; however,
there is a very high degree of uncertainty in the estimates that
undermines any general conclusion regarding a pacifying effect.

[^gp]: The 80 percent posterior credible intervals for the
    hyperparameters from the gaussian process modeling the effect of
    peace years were
    `r filter(gp, parameter == "rho") %$% interval` and
    `r filter(gp, parameter == "eta") %$% interval`
    for the length-scale ($\rho$) and the marginal standard deviation
    ($\eta$) respectively.

```{r, fig.cap = "\\label{fig:peace} Log-odds peace year intercepts - $80\\%$ CIs"}
f <- extract(reg, "f")
colnames(f) <- unique(final.df$lpeace_yrs) %>% sort

plot_pars(f, hline = T) +
    scale_x_discrete(breaks = seq(0, ncol(f), by = 4))
```

#### Interaction Effect
